### 2021-10-24 README.Rmd
Update README

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

@@

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "An accelerometer-derived ballistocardiogram method for detecting heartrates in free-ranging marine mammals"
Authors <- "Czapanskiy, M. F., Ponganis, P. J., Fahlbusch, J. A., and Goldbogen, J. A."
```

@@

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///main?urlpath=rstudio)

@@

> `r Authors` (in prep). _`r Title`_.

@@

Following publication, please cite this compendium as:

> `r Authors` (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for "`r Title`"_. Accessed `r format(Sys.Date(), "%d %b %Y")`.

@@
